%#BIBTEX biber --bblencoding=utf8 -u -U --output_safechars main
\documentclass[uplatex, dvipdfmx]{article}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{ascmac,here,txfonts,txfonts}
\usepackage[margin=2.5cm]{geometry}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{xcolor}
\usepackage[subrefformat=parens]{subcaption}
\usepackage{hyperref}
\usepackage[backend=biber, style=numeric, sorting=none]{biblatex}
\usepackage[format=hang]{caption}
\usepackage[format=hang, subrefformat=parens]{subcaption}

\captionsetup{compatibility=false}

\addbibresource{./references.bib}

\setlength{\parindent}{0.3in}

\title{修士学位請求論文要旨\\
 Iterated Inversion System: An Efficient Algorithm to Visualize Kleinian Groups Based on Inversions }
\author{中村 建斗\\
先端数理科学研究科 先端メディアサイエンス専攻\\
}

\date{}

\pagestyle{plain}

\begin{document}

\maketitle
\pagestyle{plain}
\newpage

In this paper, we introduce an efficient algorithm to visualize Kleinian
groups. Summary of each chapter is as follows.
The first chapter is Introduction. 

Kleinian groups theory is one of the fields of mathematics.
It is advanced by mathematicians in the nineteenth century.
Felix Klein and his student, Robert Fricke studied M\"obius
transformation groups.
Henri Poincare named such groups \textit{Kleinian Groups}.
Kleinian group is suited to visualization and computer experiments.
Henri Poincare named such groups \textit{Kleinian Groups}.

M\"obius transformation group is well suited to visualization and
experiment; Actually, Klein and his students also leave beautiful
visualized images of a Kleinian group without a computer.
There are aspects that mathematicians advance research from
visualization and experiment.

%% なにが問題か 既存のアルゴリズムでは足りない部分がある
%% それをIISで解決．


%% 2
The second chapter is Preparation.
We introduce terminology and some mathematical terms.
They are an inversion in circle, 
M\"obius transformations, Kleinian groups, and limit set.
%% 3
The third chapter introduce visualization of Kleinian groups.
In the chapter 3.1, basic method of Kleinian groups.
It has some defective to visualize Kleinian groups.
To solve this problem,
In chapter 3.2, we introduce the Iterated Inversion System (IIS).
It can be used two and three dimensional.
In chapter 3.3, we show the algorithm to draw three dimensional
objects using IIS.
We use \textit{sphere tracing}, a kind of ray tracing algorithm.
To render three dimantional objects, Jacobian is important.

%% 4

The fourth chapter is applications.
We introduce four application of IIS.

First one is how to render the interior or exterior of the
two-dimensional circle inversion fractals.

Secondly, the method to draw edge of circles.

Thirdly
the method to generate two or three dimensional Kleinian groups with
circle or sphere inversion. It enable us to tweak parameters of M\"obius
transformation intuitively.
It can be extended to three-dimensional sphere inversion fractals.

Lastly, Sphairahedron fractals. Sphairahedron is polyhedron with spherical
faces. Using inversions about their faces, we can make a tiling pattern
of the sphairahedron. 
In many cases, the boundary of the tiling converge to a three
dimensional fractal. 
The fractals are also rendered using IIS algorithm.

%% 5

Finally, chapter 5 is conclusion. We introduced an efficient algorithm
called Iterated Inversion System (IIS) to visualize Kleinian groups.
However, there are also Kleinian groups, which we cannot
visualize using IIS.
Our final goal is that for all Kleinian groups, we develop this kind of
efficient algorithm and get mathematical results from obtained images.


\end{document}
