%#!uplatex main.tex

\section{Introduction}

Kleinian group theory is one of the fields of mathematics studying 
M\"obius transformation groups.
Kleinian group theory is advanced by mathematicians in the nineteenth
century.
Felix Klein and his student, Robert Fricke studied M\"obius
transformation groups.
Henri Poincare named such groups \textit{Kleinian Groups}.
Moreover, composing Geometry, Algebra, and Analysis,
Poincare built foundation of Kleinian groups theory.
Klein and Poincare were rivals to study Kleinian group theory.

In the latter half of the twentieth century, according to the achievement of William
Thurston, hyperbolic geometry is again realized as a part of modern
mathematics, and Kleinian group is also studied from the viewpoint of
modern geometry;
Then the complexity of Kleinian groups is unraveled step by step by
the technique of modern mathematics until at the present.

M\"obius transformation group is well suited to visualization and
experiment; Actually, Klein and his students also leave beautiful
visualized images of a Kleinian group without a computer.
There are aspects that mathematicians advance research from
visualization and experiment.

After a computer appeared, various visualization and calculation are
performed by computer.
Visualized images of Kleinian groups often have beautiful fractal shape.
Thus, people who love computer graphics are fascinated by complicated shapes of fractals.
For example,
\textit{Fractalforums}\footnote{\url{https://fractalforums.org/}}
community gathers many fractal enthusiasts and discusses fractals.
The fractals generated by Kleinian group theory also come up for
discussion.
In a sense, Kleinian group theory is an interdisciplinary area between
mathematics and arts.

Mumford, Series, and Write wrote a book called
\textit{Indra's Pearls} \cite{MumfordSeriesWright200204}.
This book is written for non-mathematician and contains explanations
about Kleinian group theory, many beautiful visualized images, and
methods of visualization.
Thus, not only math maniacs but also programmers enjoy the book and
Kleinian groups.

However, the book deal with only a small part of Kleinian group.
Because, the number of combinations of the elements of the group
exponentially increases, it is difficult to
visualize all of the types of Kleinian groups in real time
in spite of the growth of the performance of a personal computer.

Our final goals are to visualize all of the Kleinian groups in real time by
personal computer and help us understand the Kleinian group theory
intuitively with software.
As the first step to the goals, we invent an algorithm called
\textit{Iterated Inversion System (IIS)}.
IIS is an algorithm to render Kleinian group based on circle or sphere
inversions.
It visualizes not only three-dimensional Kleinian group but also
four-dimensional Kleinian group.
In this paper, we introduce the basic usage of the IIS algorithm and its
applications.

