%#BIBTEX biber --bblencoding=utf8 -u -U --output_safechars main
\documentclass[uplatex, dvipdfmx]{article}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{ascmac,here,txfonts,txfonts}
\usepackage[margin=2.5cm]{geometry}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}
\usepackage{xcolor}
\usepackage[subrefformat=parens]{subcaption}
\usepackage{hyperref}
\usepackage[backend=biber, style=numeric, sorting=none]{biblatex}
\usepackage[format=hang]{caption}
\usepackage[format=hang, subrefformat=parens]{subcaption}

\captionsetup{compatibility=false}

\addbibresource{./references.bib}

\setlength{\parindent}{0.3in}

\title{ Iterated Inversion System: An Efficient Algorithm to Visualize Kleinian Groups Based on Inversions }
\author{ Kento Nakamura\\
Meiji University\\
}

\date{}

\pagestyle{plain}

\begin{document}

\maketitle
\pagestyle{plain}


\begin{abstract}
 Kleinian group is one of the fields of mathematics. Visualized
 Kleinian group shows us beautiful fractal structure, and clues to
 understand their mathematical properties.
 However, it often takes much time to render Kleinian group.
 Thus, we invent an efficient algorithm to visualize Kleinian groups. 
 The algorithm is called Iterated Inversion System
 (IIS.) It can render not only two dimensional objects but also three
 dimensional objects.
 We summarize the usage of the IIS and its applications.
\end{abstract}

\clearpage

\tableofcontents

\clearpage

\input{introduction}

\input{preparation}

\input{visualization}

\input{application}

\input{conclusion}

\section*{Acknowledgement}
We thank our super visor, Kazushi Ahara.

Our family.

Meiji University

\addcontentsline{toc}{section}{References}
\printbibliography

\end{document}
