%#BIBTEX biber --bblencoding=utf8 -u -U --output_safechars main
%#!uplatex main.tex

\section{Preparation}

In this section, we introduce some mathematical terms and prerequisites
to understand the IIS algorithm and basic usage of IIS.

\subsection{Terminology}
%\subsection{Transformation group theory}

In this paper, we use terms about Kleinian groups used in Indra's
Pearls \cite{MumfordSeriesWright200204}.
The word \textit{group} represents an algebraic group which is
central concept about group theory.
Algebraic group is a set which has multiplication, satysfies the
associative law, has a unit, and has an inverse element for each
element.

%Also, a transformation group is an algebraic group consists of transformations 
%on a topological set $X$.  Here a transformation is a homeomorphism $f:X \to X$.
Also, a transformation group is an algebraic group consists of transformations 
about plane or space.

%\par We will introduce the M\"obius transformation group and Kleinean group as a subgroup of the M\"obius transformation group.

%In this paper, we mainly consider the cases $X=\tilde{\mathbb{C}}$, which is the union of the complex set and the infinity, 
%and $X=\tilde{ \mathbb{R} }^3$, which is the union of $\mathbb{R}^3$ and the infinity.
%In our context we suppose proper topologies on $\tilde{\mathbb{C}}$ by the omplex topology of $P^1(\mathbb{C})$ and on $\tilde{ \mathbb{R} }^3$ by one-point compactification from $\mathbb{R}^3$ respectively.
However, in this case, because we assume M\"obius transformation
group, we add infinity $\infty$ to complex plane $\mathbb{C}$ (or three
dimensional space $\mathbb{R}^3$) and apply one-point compactification
to the set. \par
Here we consider the plane or the space with the infinity $\infty$. 
That is, we consider the one-point compactification of $\mathbb{C}$ and
it is denoted by $\tilde{\mathbb{C}}$. 
In the same way, the one-point compactification of $\mathbb{R}^3$ is 
denoted by $\tilde{ \mathbb{R} }^3$.

%\par We will introduce M\"obius transofmation group on $\tilde{\mathbb{C}}$ and $\tilde{ \mathbb{R} }^3$.  
% First, the two dimensional M\"obius transformation group
% \textrm{M\"ob}$(\tilde{\mathbb{C}})$ is the set of linear fractional transformations $f(z)=\frac{az+b}{cz+d}$, 
% where $a,b,c,d$ are complex numbers and they satisfy $ad-bc = 1$. Here we naturally extend a complex function $f(z)$ 
% into a transformation on $\tilde{\mathbb{C}}$.  
% A linear fractional transformation is a conformal orientation-preserving homeomorphic map.
% See also section *.* .
% From another point of view, a M\"obius transformation is the composition of even number of circle inversions.  
% About inversions, see section *.* .
% In the same manner, we consider the three dimensional M\"obius
% transformation group \textrm{M\"ob}$(\tilde{\mathbb{R}}^3)$
% In the three dimensional case, we define a M\"obius transformation as the composition of even number of sphere inversions.
The two dimensional M\"obius transformation group
\textrm{M\"ob}$(\tilde{\mathbb{C}})$
is the set of M\"obius transfromation. 
The definition of a M\"obius transformation will be introduced later. 
This is a group with respect to the composite of transformations.
The unit is the identity map and the inverse element is the 
inverse transformation. 
In the same manner, we consider the three dimensional M\"obius
transformation group
\textrm{M\"ob}$(\tilde{\mathbb{R}}^3)$

\subsection{Inversions in Circles or Spheres}

% In the two dimensional case, it is well known that M\"obius transformations on $\tilde{\mathbb{C}}$
%are composed of even number of circle-inversions and line-symmetries.
%Here, if a circle is centered at $C\in\mathbb{C}$ and it has a radius $R\in\mathbb{R}$ ($R>0$).
% Then the formula of the inversion along the circle is given by
%$f(z) = \frac{R^2}{~\overline{z -C}~} + C$.
%Since $f \circ f$ is the identity map, the inversion map is a homeomorphism on $\tilde{\mathbb{C}}$.
% Remark that the inversion is an orientation-reversing conformal map on $\tilde{\mathbb{C}}$.
It is known that M\"obius transformations on $\tilde{\mathbb{C}}$
are composed of even number of inversions in circles.
Here, it is assumed that the inverse mapping about circle centered at
$C\in\mathbb{C}$ and radius $R\in\mathbb{R}$ ($R>0$).
The formula is given by
$f(z) = \frac{R^2}{~\overline{z -C}~} + C$.
According to the definition, inverse mapping is a homeomorphic mapping on
$\tilde{\mathbb{C}}$.

% We often distinguish the inversion from a line symmetry map.
%But in this context, by interpreting the line on the complex plane as a circle centered at the infinity, 
%we may regard the line symmetry as a kind of the inversion. 
%In the sequel, we will call inversion both of circle-inversions and line-symmetries.
%In this category, any inversion is orientation-reversing, conformal, and homeomorphic on $\tilde{\mathbb{C}}$.
In this context, the circles do not center infinity, but 
by interpreting the line on complex plane as ``the circle whose center is
infinitely far point and radius is infinity'', 
line symmetry transformation (but infinitely far point is
transformed to infinitely far point) on complex plane 
is also inversion in the circle.
Inversion mapping (including line symmetry transformation) does not
preserve direction of complex plane.
Thus compositions of even number of inversion mapping are homeomorphic
mappings preserving direction of complex plane.

%\par Here we will make a short note on the Jacobian of inversion.
% If the inversion is a line symmetry, the determinant of the Jacobian is $-1$.
% Otherwise if the inversion is a circle-inversion, remarking that a circle inversion
% preserve any angles, we obtain that Jacobian mapping is given by the composition of multiplication by a complex constant
% and complex conjugate.
% Thus the determinant of the Jacobian at a point $P\in\mathbb{C}$ is given by the following formula:
% \[ \mathrm{Det}(\mathrm{Jacobian}) = R^4 / distance(P,~C)^4 \]%
% Here the Jacobian is a composition of a scaling and a rotation and a complex conjugate, and we obtain the following.
% \[ \mathrm{scaling factor at } P  = R^2 / distance(P,~C)^2. \]
Later, we compute Jacobian of inverse mapping.
This is Jacobian matrix as mapping from complex plane to complex plane.
Generally, inverse mapping preserve angles.
From this property, Jacobian mapping is given by multiplication of complex
number.
Concretely, Jacobian is composed of rotations and constant scaling
and absolute value of Jacobian is as follows
$Jacobian = R^2 / distance(P,~C)^2$
where $P$ is a point before applying the inversion.

%\par In the similar way as the definition of a circle-inversion,
% a sphere-inversion can be defined as follows.
% Fix a sphere $C$ in $\mathbb{R}^3$.  Let its center be $C$ and its radius be $R$. 
% A sphere-inversion $I_C$ is a homeomorphism on $\tilde{\mathbb{R}}^3$ 
% determined by a map from a point $P$ to a point $Q = I_C(P)$ such that (i) $Q$ is on the half line $CP$ and 
% that (ii) $\overline{CP}\cdot \overline{CQ} = R^2$.
% As above, the definition of a circle-inversion can be extended to a plane-symmetry
% in the same way as a line-symmetry in the two dimensional case.
In the similar manner to circle inversions we can determine inversion
mapping about spherical surface $S^2$ included in $\tilde{\mathbb{R}}^3$.
Here, image of the inversion mapping is determined by center of the sphere and
distance to the center.
Concretely, $f(z) = \frac{R^2}{~\overline{z -C}~} + C$.
Also, a plane $\alpha$ included in $\mathbb{R}^3$ is considered as
sphere whose center and radius are infinity.
In this case, the inversion mapping about the plane $\alpha$ is plane symmetry
transformation about $\alpha$.

%\subsection{M\"obius transformations and the hyperbolic geometry}
\subsection{M\"obius Transformations}

% First we review the definition of a group action. 
% Let $G$ be a group and $X$ be a set. A map $G \times X \to X : (g,x) \mapsto g\cdot x$
% is called a $G$-action on $X$ if it satisfies the following conditions.
% \par \qquad (1) $e \cdot x = x$ for all $x \in X$. (Here, $e$ denotes the unit of $G$.)
% \par \qquad (2) $(gh) \cdot x = g \cdot (h\cdot x)$ for all $g, h \in G$ and for all $x \in X$.

% In this study, we handle $PSL_2\mathbb{C}$-action on $\hat{\mathbb{C}}$.
% Here $PSL_2\mathbb{C}$ is the projective space of $2 \times 2 complex matrices $A$ with $\mathrm{det}(M)=1$. 
% M\"obius transformation is defined as a linear fractional transformation
%$f(z)=\dfrac{az+b}{cz+d}$ for complex variable $z$ where constants
%$a, b, c, d$ are complex numbers and satisfy $ad - bc = 1$.
In this study, we handle actions on $PSL_2\mathbb{C}$ of $\hat{\mathbb{C}}$.
M\"obius transformation is defined on $\hat{\mathbb{C}}$ and
linear fractional transformation
$f(z)=\dfrac{az+b}{cz+d}$ for complex variable $z$ where constants
$a, b, c, d$ are complex number and satisfy $ad - bc = 1$.
Such linear fractional transformation $f(z)$ is conformal homeomorphic
mapping and preserves direction of $\hat{\mathbb{C}}$.

%\par If we consider a map %\varphi: \dfrac{az+b}{cz+d} \mapsto $\begin{pmatrix}a & b \\ c& d \end{pmatrix}$,
% from the set of linear fractional transformations to $PSL_2\mathbb{C}$.
% This map $\varphi$ is a group isomorphism and it gives an induced action of $PSL_2\mathbb{C}$ on $\hat{\mathbb{C}}$.
% In the sequel, we regard the action of linear fractional transformations
% and that of $PSL_2\mathbb{C}$ without distinction.
% For more details about M\"obius transformation, refer
% \cite{MumfordSeriesWright200204}\cite{marden_2016}.
As a group acting on $\hat{\mathbb{C}}$, a set of linear fractional
transformation $f(z) = \dfrac{az + b}{cz + d}$
and a set of $2 \times 2$ matrix
$\begin{pmatrix}a & b \\ c& d \end{pmatrix}$
$PSL_2\mathbb{C}$ are same type.
So, in this place, we use linear fractional transformation and
complex two-dimensional projective special linear group
$PSL_2\mathbb{C}$ without distinction.
Also it is known that any M\"obius transformation can be represented by
even number of circle inversions.
The compositions of M\"obius transformations is also M\"obius
transformations. A set of all of the M\"obius transformations makes
groups. For more details about M\"obius transformation, refer
\cite{MumfordSeriesWright200204}\cite{marden_2016}.
In this sense, a set of the linear fractional transformations acts on
$\hat{\mathbb{C}}$.

% M\"obius transformation is deeply related to the hyperbolic geometry.
% When all of the coefficients in $f(z) = \dfrac{az + b}{cz + d}$
% are real number, $f(z)$ preserve upper-half plane.
% Moreover, $f(z)$ preserves the hyperbolic metric $\dfrac{dz^2}{(\mathrm{Im}z)}$
% on the upper-half plane.
% Such linear fractional transformations corresponds to an element of $PSL_2\mathbb{R}$.
% Thus the $PSL_2\mathbb{R}$-action on the upper half plane is
% the isometric transformation group of the hyperbolic plane $\mathbb{H}^2$.
When all of the constant numbers of M\"obius transformations are real number,
that is, $a, b, c, d \in \mathbb{R}$, $f(z)$ preserve upper-half plane.
Moreover, Metric of upper-half plane preserves
$\dfrac{ds^2}{(\mathrm{Im}z)}$.
Thus, a set of linear fractional transformations whose all of constants
are real number acts on hyperbolic plane as an isometric transformation group.

%\par When the coefficients $a, b, c, d$ are complex numbers, 
% the action can be thought as an isometric transformation group on the hyperbolic space $\mathbb{H}^3$.
% We consider the upperhalf model of the hyperbolic space $\mathbb{H}^3$.
% In fact, 
% \[\mathbb{H}^3 = \{ (z,t) \in \mathbb{C}\times \mathbb{R}\mid t>0 \} \cup \{\infty\} \]
% is the upper half model with the hyperbolic metric $\dfrac{dz^2+dt^2}{t^2}$ and 
% $\hat{\mathbb{C}} = \{ (z,0) \mid z \in \mathbb{C}\} \cup \{ \infty\}$
% is the set of infinity. The two dimensional M\"obius transformation group acts on $\hat{\mathbb{C}}$
% naturally and it is well known that this action can be extend to 
% an action on the upper half model as isometric transformations.
% This extension is called \lq Poincar\'e extension\rq.
% As above, researching structures of the M\"obius transformation groups is heavily
% related to studying three-dimensional hyperbolic geometry and hence hyperbolic manifolds.
% For more details, refer 
% \cite{Marden200705outerCircles}\cite{taniguchi_okumura199610invitation}.
When the constants $a, b, c, d$ are complex number, it is thought that
$f(z)$ acts on hyperbolic space.
As the model of hyperbolic space $\mathbb{H}^3$, we consider upper half
space model, but we consider three-dimensional space as the coordinates
$(z, t)$, and $z$ is complex coordinates and $t$ is real coordinates.
Upper-half space model is a model of hyperbolic space whose universal
set is $\{(z,t) \mid t>0\}\cup \{ \infty \}$.
$\hat{\mathbb{C}} = \{ (z,0) \mid z \in \mathbb{C}\} \cup \{ \infty\}$
is its set of infinitely far points. M\"obius transformations are groups acting on
the set of infinitely far points. However, it is known that by Poincare
expansion, M\"obius transformations are extended to isometric mapping
in hyperbolic space.
For the relationship between M\"obius transformations and hyperbolic
space, refer 
\cite{Marden200705outerCircles}\cite{taniguchi_okumura199610invitation}.

% In this paper, we also consider the three dimensional M\"obius
% transformation on $\hat{\mathbb{R}^3} = \mathbb{R}^3\cup\{\infty\}$.
% The definition of the three dimensional M\"obius transformation in the two ways as follows.
% One is the simple extension of the two dimensional version.
% A M\"obius transformation is defined as a composition of even number of sphere-inversions 
% and plane-symmetry.
% The other is the representation of the isometry group of the four dimensional hyperbolic space.
% To represent three-dimensional M\"obius transformation using matrix,
% we consider a quaternion $2 \times 2$ matrix group called
% $Sp^k(1,1)$. About this topic, refer
% \cite{sakugawa2010limit}\cite{sakugawa2007master}.
In this paper, we also use a concept extending a M\"obius
transformation to a $\mathbb{R}^3\cup\{\infty\}$.
Concretely, we define composition of even number of inversion mapping
about a sphere as a three-dimensional M\"obius transformation.
The definition is extended relation between inversions in a circle and
M\"obius transformation.
In that sense, M\"obius transformation should be called two-dimensional
M\"obius transformation, but
simply they are called differently M\"obius transformation and
three-dimensional M\"obius transformation without confusion.

% Three-dimensional M\"obius transformations are deeply related to
% the four-dimantional hyperbolic space. In fact, the upper-half space model of
% the four-dimensional hyperbolic space $\mathbb{H}$ is homeomorphic to the 
% four-dimensional open ball and its boundary (the infinity point set of the hyperbolic
% space) is $\hat{\mathbb{R}^3} = \mathbb{R}^3\cup\{\infty\}$.
% Using Poincar\'e extension, a sphere-inversion in $\hat{\mathbb{R}^3}$
% is extended to an (orientation-reversing) isometric transformation of $\mathbb{H}^4$.
% Thus the composition of even numbers of sphere-inversions corresponds to an orientation-preserving
% isometry, and it is known that any isometry of $\mathbb{H}^4$ is given in this way.
% In this point of view, three-dimensional M\"obius transformations are
% deeply related to the four-dimensional hyperbolic space and four-dimensional hyperbolic manifolds.
Three-dimensional M\"obius transformations are deeply related to
four-dimantional hyperbolic space. Actually, we assume four-dimensional
hyperbolic upper half space model, its infinite far point set is
$\mathbb{R}^3\cup\{\infty\}$, and it is known that three-dimensional M\"obius
transformation gives orientation preserving isometric transformation in
four-dimensional hyperbolic space via poincare expansion.
In this sense studying three-dimensional M\"obius transformation is
deeply related to four-dimensional hyperbolic space or four-dimensional
hyperbolic space and four-dimensional hyperbolic polyhedra.
To represent three-dimensional M\"obius transformation using matrix
there are Quaternion matrix sub-group of $2 \times 2$ matrix called
$Sp^k(1,1)$. About this topic, refer
\cite{sakugawa2010limit}\cite{sakugawa2007master}.

\subsection{Classification of M\"obius Transformations}

% Excluding the identical map, we will classify M\"obius transformations
% $f(z) = \dfrac{az + b}{cz + d}$ into three types.
% The types are \textit{elliptic}, \textit{parabolic}, and \textit{loxodromic}.
% It is well-known that the standard form of $PSL_2\mathbb{C}$
% is either one of $\begin{pmatrix}1 & \lambda \\ 0 & 1 \end{pmatrix}$(, $\lambda$ is a non-zero constant,) or
% $\begin{pmatrix}\lambda & 0 \\ 0 & \lambda^{-1} \end{pmatrix}$(, $\lambda$ is a non-zero constant,) 
% from a famous theorem in linear algebra.
% If $X=\begin{pmatrix}a & b \\ c & d \end{pmatrix}$ is conjugate to the former one,
% then $f(z)$ is called a parabolic transformation.
% If $f(z)$ is parabolic, the number of fixed point is one, and
% the matrix $X$ satisfy $\mathrm{tr}^2X = 4$.
Excluding the identical mapping, M\"obius transformations
$f(z) = \dfrac{az + b}{cz + d}$ are classified as three types.
They are \textit{Elliptic}, \textit{Parabolic}, and \textit{Loxodromic}.
By the knowledge of linear algebra, the standard form of $PSL_2\mathbb{C}$
is either one of $\begin{pmatrix}1 & a \\ 0 & 1 \end{pmatrix}$ or
$\begin{pmatrix}\lambda & 0 \\ 0 & \lambda^{-1} \end{pmatrix}$.
The former one of $f(z)$ is parabolic transformations.
For parabolic transformation the number of fixed point is one, and
$2 \times 2$ square matrix $X$ satisfy $\mathrm{tr}^2X = 4$.

%\par When the standard form of $X$ is
% $\begin{pmatrix}\lambda & 0 \\ 0 & \lambda^{-1} \end{pmatrix}$,
% we have the following two cases. 
% One is the case $|\lambda|=1$ and the other is the case $|\lambda|\neq 1$ 
% If $|\lambda|=1$ then $f(z)$ is called an elliptic transformation.
% When $f(z)$ is elliptic,  the fixed point set of $f(z)$ consists of two distinct points,
% and $f(z)$ gives a rotation around these fixed points.
% And $f(z)$ is elliptic if and only if $\mathrm{tr}^2X > 4$.
% Remark that if the order of a M\"obius transformation $f(z)$ is finite
% then it is elliptic.
When the standard form is
$\begin{pmatrix}\lambda & 0 \\ 0 & \lambda^{-1} \end{pmatrix}$
or absolute value of lambda is one, that is  $|\lambda|$ is $1$, 
$f(z)$ is called elliptic transformations.
The properties of elliptic transformation are they have
two fixed points and the transformation gives rotations around fixed
points.
Also, the matrix representation $\mathrm{tr}^2X > 4$ is 
necessary and sufficient conditions.
In addition, the m\"obius transformation having finite order
is elliptic transformation.

%\par If the standard form is
% $\begin{pmatrix}\lambda & 0 \\ 0 & \lambda^{-1} \end{pmatrix}$
% with $|\lambda| \neq 1$, then $f(z)$ is called a loxodromic transformation.
% In a special case, if $\lambda$ is real number other than $\pm 1$, the transformation is called
% a \textit{hyperbolic} transformation too.
% When $f(z)$ is loxodromic the number of the fixed point set of $f(z)$ is two.
% One of the fixed points is called an attracting fixed point and the other is called a 
% repelling fixed point. This is because the orbid space of $f(z)$ of a general point $z_0$
% has two limit point and one of two is the limit of $f^n(z_0)$ for $n\to \infty$, and the other
% is the limit of $f^n(z_0)$ for $n\to -\infty$.
% Also, $f(z)$ is loxodromic if and only if $\mathrm{tr}^2X < 4$.
When the standard form is
$\begin{pmatrix}\lambda & 0 \\ 0 & \lambda^{-1} \end{pmatrix}$
and complex number $|\lambda| \neq 1$, $f(z)$ is called loxodromic.
If $\lambda$ is real number exclude in $1$, the transformation is called
\textit{hyperbolic} too.
The properties of loxodromic transformation are they have two fixed
points. One of the fixed points is attracting and the other one is repelling.
Also, $\mathrm{tr}^2X < 4$ is necessary and sufficient conditions.

%\par The set of three-dimensional M\"obius transformations also have a similar
% classification into six types.
% In three dimensional case, each types \lq parabolic\rq, \lq elliptic\rq, \lq loxodromic\rq has 
% a modifier \textit{simple} and \textit{compound}.
% Thus there are six variations of classification types, for example \lq\lq simple elliptic\rq\rq or
% \lq\lq compound loxodromic\rq\rq.
% For detailed information of classfication of three dimensional M\"obius transformation, see chapter 4.3.2.
For three-dimensional transformations also have this kind of
classification.
In this case, it is added \textit{simple} or \textit{compound} and
there are six variations of classification like ``simple elliptic'' or
``compound loxodromic''.
For detailed, see chapter 4.3.2.

%%***************ここまでみた20190111-2127****


\subsection{Kleinian Groups}

Kleinian groups are groups originated from name of Felix Klein who is
a mathematician in nineteenth century.
The group $G$ is Kleinian group when it satisfies following two
conditions. 
Firstly, $G$ should be a sub-group of M\"obius transformation group.
Secondly, about a fixed point $x\in\mathbb{H}^3$ in hyperbolic space,
its orbit space $Gx = \{ gx \mid g\in G\}\subset \mathbb{H}^3$
is properly discontinuous.
In this place, sub-set $A$ of hyperbolic space $\mathbb{H}^3$
is properly discontinuous means
for any compact set $K$ of $\mathbb{H}^3$,
there are only finite number of $\gamma$ which is element of $A$
and becomes $\gamma (K) \cap K \neq \phi$.

When a point $x$'s orbit space is properly discontinuous, we take
fundamental domain whose volume is plus.
Considering M\"obius transformation gives isometric transformation of
hyperbolic space, we also consider tiling of hyperbolic space by
Kleinian groups. 

In this paper, we consider M\"obius transformation widely and
think about a mapping which is represented by a composite mapping of
inversion mapping (not limited to even number).
As a term, to distinguish original M\"obius transformation
we call them \textit{extended M\"obius transformation}.
A composite mapping composed of odd number of inversion mapping
is represented by $f(z)=\dfrac{a{\bar{z}}+b}{c{\bar{z}}+d}$ where
$a, b, c, d$ are complex number and $ad-bc = 1$.
However, $\overline{z}$ represents conjugation of complex number.

Extended M\"obius transformation introduced isometric mapping (not
necessarily preserve direction) on three-dimensional hyperbolic space by
poincare expansion.
Properly discontinuous sub-group of extended M\"obius transformation group
is called \textit{extended Kleinian groups}.
Basic property of Kleinian group is described in chapter 2 of \cite{marden_2016}.

\subsection{Limit Set}

Let Kleinian group be $\Gamma$.
We call closed set of all of the limit point \textit{limit set}.
Also, We represent it as $\Lambda(\Gamma)$.
There are some known properties about limit set.
For example,
\begin{itemize}
 \item The orbit space of fixed points of generators becomes limit set.
 \item A point on the limit set transformed by element of the group 
       also a point on the limit set.
 \item Fixed points of generators become limit set.
\end{itemize}

Infinite words $\overline{ab}$ converge to it is called \textit{algebraic limit.}
\textit{geometric limit} is a set of transformed points converging to
the limit.

The property of the limit set is also described in chapter 2.4.1 of
\cite{marden_2016}.

% In this paper, for simplicity, we use
% lower case alphabets such as $a$ and $b$ instead of $f(z)$ and $g(z)$ and
% upper case alphabet such as $A$ and $B$ instead of $f^{-1}(z)$ and $g^{-1}(z)$

% From this point, we assume transformation group $G$ is generated by two
% elements $a$ and $b$. Arbitrary elements of $G$ is represented by
% four alphabet $a$, $b$, $A$, and $B$ and we follow the rule of inverse
%  of $a$ is $A$ and inverse of $b$ is $B$.
% Thus, composite mapping $f(z)\circ g(z) \circ f^{-1}(z)$ simply
% is represented by $abA$.

% Following the rule of the words, we represent circular infinite words as
% bar, that is, $aaaa\cdots$ is represented by $\overline{a}$ and $abABabAB \cdots$ 
% is represented by $\overline{abAB}$.
% These infinite words are not element of $G$. However, when we consider
% the orbit by $G$, we use such notations to express the limit set.
